### 2021-07-14 src/paper/model/code.tex
Finish going over appendix B. More type corrections, suggestions and comments.
Finish most things in section B.

The code used for this paper is open source and available under the MIT License. It is
split into two parts
\begin{itemize}
    \item The code for the model can be found at
   \href{https://github.com/covid-19-impact-lab/sid/}{https://github.com/covid-19-impact-lab/sid/}
   and its documentation at
   \href{https://sid-dev.readthedocs.io}{https://sid-dev.readthedocs.io}.
   \item The code for the application to Germany can be found at
   \href{https://github.com/covid-19-impact-lab/sid-germany/}{https://github.com/covid-19-impact-lab/sid-germany/}
   with a shorter documentation at
   \href{https://sid-germany.readthedocs.io}{https://sid-germany.readthedocs.io}.
\end{itemize}

>>>>

\subsection{Reproducibility}
\label{subsec:code}

The source code used for this paper is open source and available under the MIT License.
It is split into two parts
\begin{itemize}
    \item The source code for the model can be found at
   \href{https://github.com/covid-19-impact-lab/sid/}{https://github.com/covid-19-impact-lab/sid/}
   and its documentation at
   \href{https://sid-dev.readthedocs.io}{https://sid-dev.readthedocs.io}.
   \item The source code for the application to Germany can be found at
   \href{https://github.com/covid-19-impact-lab/sid-germany/}{https://github.com/covid-19-impact-lab/sid-germany/}
   with a shorter documentation at
   \href{https://sid-germany.readthedocs.io}{https://sid-germany.readthedocs.io}.
\end{itemize}

### 2021-07-14 src/paper/model/course_of_disease.tex
Finish most things in section B.

We allow the progression of the disease to be stochastic in two ways: Firstly, state
changes only occur with a certain probability (e.g. only a fraction of infected
individuals develops symptoms). Secondly, the number of periods for which an individual
remains in a state is drawn randomly. The parameters that govern these processes are
taken from the literature and detailed in Section~\ref{sub:data_course_of_disease}. For
an overview of our disease progression parameters see
Table~\ref{tab:disease_and_vacc_model}.\comment[id=K]{@Janos: Is this what you wanted
("Replace this by a link to the relevant table with parameters in the data appendix, once
we have that table")}

>>>>

We allow the progression of the disease to be stochastic in two ways: Firstly, state
changes only occur with a certain probability (e.g. only a fraction of infected
individuals develops symptoms). Secondly, the number of periods for which an individual
remains in a state is drawn randomly. The parameters that govern these processes are
taken from the literature and detailed in Section~\ref{sub:data_course_of_disease}. For
an overview of our disease progression parameters see
Table~\ref{tab:disease_and_vacc_model}.

### 2021-07-14 src/paper/model/matching.tex
Finish most things in section B.

%% Recurrent contacts ============================================================
Recurrent contacts are described by two components: 1) A set of time invariant groups,
such as school classes or groups of co-workers. Those groups are generated once at the
beginning of the simulation. The groups can be sampled from empirical data or created by
randomly matching simulated individuals into groups. 2) A deterministic or random
function that takes the value 0 (non-participating) and 1 (participating) and can depend
on the weekday, date and health state.\comment[id=K]{Actually the full states and params
enter into the contact functions} This can be used to model things like vacations,
weekends or symptomatic people who stay home (see section \ref{sec:policies} for
details).

@@

The matching of non-recurrent contact types is more difficult because the contact network
is resampled randomly every day. Moreover, it needs to allow for assortative matching. In
our application, all random contacts are assortative with respect to age group $a$ (it is
usually more likely to meet people from the same age group) and county (it is more likely
to meet people from the same county) but in principle any set of discrete variables can
be used. This set of variables that influence matching probabilities
\replaced[id=K]{induce}{introduce} a discrete partition of the population into groups.

>>>>

%% Recurrent contacts ============================================================
Recurrent contacts are described by two components: 1) A set of time invariant groups,
such as school classes or groups of co-workers. Those groups are generated once at the
beginning of the simulation. The groups can be sampled from empirical data or created by
randomly matching simulated individuals into groups. 2) A deterministic or random
function that takes the value 0 (non-participating) and 1 (participating) and can depend
on the weekday, date and health states of the entire population. This can be used to
model things like vacations, weekends or symptomatic people who stay home (see section
\ref{sec:policies} for details).

@@

The matching of non-recurrent contact types is more difficult because the contact network
is resampled randomly every day. Moreover, it needs to allow for assortative matching. In
our application, all random contacts are assortative with respect to age group $a$ (it is
usually more likely to meet people from the same age group) and county (it is more likely
to meet people from the same county) but in principle any set of discrete variables can
be used. This set of variables that influence matching probabilities induce a discrete
partition of the population into groups.

### 2021-07-14 src/paper/model/policies.tex
Finish most things in section B.

The most complex policies are typically found in the education sector. Since the
beginning of \replaced[id=K]{2020}{2021} schools have switched back and fourth between
full closures, split class approaches with alternating schedules for some or all age
groups and reopening while maintaining hygiene measures. On top of that there are
different policies for allowing young students whose parents work full time to attend
school even on days where they normally would not. For details on how we calibrate these
policies see Section~\ref{subsec:policies}.\comment[id=K]{Did I write enough on the school policies? (No sources or details so far...)}

Importantly, policies can depend on the health states of participating individuals.
\replaced[id=K]{Thus, it would be possible}{This allows} to quarantine entire school
classes if one student tested positive \replaced[id=K]{and many other forms of contact
tracing}{or to implement official or private contact tracing}.

For some policies the exact effect on each contact type is not easy to determine. If this
refers to a policy that has been active during the estimation period, it is possible to
estimate such parameters by fitting the model to time series data of infection rates.
This is only possible if the policy was not active during the whole estimation period and
thus the infection probabilities can be identified separately. We do this to account for
hygiene measures at school and in the workplace that have been in effect since November
2020.\comment[id=K]{I don't understand this paragraph.}

Not all things that reduce contacts compared to the pre-pandemic level are driven by
NPIs. Therefore, we also model endogenous contact reductions that can depend on the
health state of individuals \replaced[id=K]{}{, known risk contacts} or the local
incidence. Examples in our model are contact reductions for symptomatic individuals or
those who have a positive PCR or rapid tests \replaced[id=K]{or contact reductions when a
household member tested positive}. The extent to which contacts are reduced can be
calibrated from surveys. For an application of our model showcasing private contact
tracing in the context of the Christmas holidays see \cite{Gabler2020}.

>>>>

The most complex policies are typically found in the education sector. Since the
beginning of 2021 schools have switched back and fourth between full closures, split
class approaches with alternating schedules for some or all age groups and reopening
while maintaining hygiene measures. On top of that there are different policies for
allowing young students whose parents work full time to attend school even on days where
they normally would not. For details on how we calibrate these policies see
Section~\ref{subsec:policies}.

Importantly, policies can depend on the health states of participating individuals. For
example children rarely go to school when they have symptoms. It would even be possible
to quarantine entire school classes if one student tested positive and many other forms
of contact tracing. For an application of our model showcasing private contact tracing in
the context of the Christmas holidays see \cite{Gabler2020}.

Not all things that reduce contacts compared to the pre-pandemic level are driven by
NPIs. Therefore, we also model endogenous contact reductions that depend on the health
state of individuals. Other possible factors could include things such as the local
incidence. The extent to which contacts are reduced can be calibrated from surveys.

### 2021-07-14 src/paper/model/summary.tex
Finish most things in section B.

To predict and quantify the effects of a wide variety of fine-grained social distancing
policies, vaccinations and rapid testing, we propose a different model structure. Our
model inherits many features from prototypical agent-based simulation models but
replaces the contacts between moving particles by contacts between individuals who work,
go to school, live in a household and enjoy leisure activities.

The structure of the model is depicted in Figure~\ref{fig:model_contacts_infections}.

We distinguish between eight types of contact
models which are all listed in Figure~\ref{fig:model_contacts_infections}: households,
recurrent and random work contacts, recurrent and random leisure contacts, and nursery,
preschool, and school contacts.

@@

After rapid tests become available, people who work or go to school can receive rapid
tests there. Moreover, people can decide to make a rapid test if they develop symptoms,
have many planned contacts or observe cases in their contact network. People who have a
positive rapid test demand a confirmatory PCR test with a certain probability. Moreover,
PCR tests can be demanded because of symptoms or randomly.

@@

People who have symptoms, received a positive test, or had a risk contact can reduce
their number of contacts across all contact types endogenously. The extent to which this
is done is calibrated from survey data.

>>>>

We use an agent-based simulation model with detailed contact networks. The model
structure is depicted in Figure~\ref{fig:model_contacts_infections}.

We distinguish between eight types of contacts which are all listed in
Figure~\ref{fig:model_contacts_infections}: households, recurrent and random work
contacts, recurrent and random leisure contacts, as well as nursery, preschool, and
school contacts.

@@

After rapid tests become available, people who work or go to school can receive rapid
tests there. Moreover, people can decide to do a rapid test if they develop symptoms,
have many planned contacts or have a sick or positively tested household member. People
who have a positive rapid test demand a confirmatory PCR test with a certain probability.
Moreover, PCR tests can be demanded because of symptoms or randomly.

@@

People who have symptoms or received a positive test can reduce their number of contacts
across all contact types endogenously. The extent to which this is done is calibrated
from survey data.

### 2021-07-14 src/paper/model/testing.tex
Finish most things in section B.

 \comment[id=K]{Talk here about reactions to tests
and symptoms with contact reductions. (If not here, find other place where to talk about
this in detail.)}

Having a realistic model of PCR and rapid tests is crucial for two reasons: Firstly, only
via a testing model can the simulated infections from the model be made comparable to
official case numbers. Secondly, individuals with undetected or not yet detected
infections are an important driver of the pandemic: \textcolor{blue}{One of the features
that makes SARS-CoV-2 so hard to control is that it can be transmitted both by pre- and
asymptomatic individuals which makes it difficult for individuals to isolate when they
pose a risk to others. Our model captures this because developing symptoms or receiving a
positive test result leads many people to reduce their contacts, especially contacts
outside the own household.}\comment[id=K]{I think these multipliers $\tau$ are not
mentioned in the data section.}

@@

Therefore, we \replaced[id=K]{build}{aim for} a simpler model of PCR and rapid tests that
can be calibrated with available data on test demand and availability and -- nevertheless
-- can produce a share of undetected cases that varies over time and across age groups
and agrees with other estimates over the time periods where they are available.

@@

Sampling uniformly from the pool of symptomatic individuals ensures that age groups who
are more likely to develop symptoms are also more likely to receive tests. Thus, the
share of detected cases is much higher for the elderly than for children in time periods
where many tests are done because of symptoms which is in line with the estimates from
the literature. \comment[id=J]{need source}

@@

The second challenge is solved by mechanistic rapid test demand models for the
workplace, schools and by private individuals. The calibration of these models is
described in Section~\ref{subsec:rapid_test_demand}.
Figure~\ref{fig:antigen_tests_vaccinations} shows that the number of performed rapid
tests in the model fits the empirical data well (where empirical data is available).
 \comment[id=K]{Maybe refer to the more detailed \ref{fig:share_rapid_test_last_week2}}

In contrast to PCR tests, rapid tests are not perfect and can be falsely positive or
falsely negative. While the specificity of rapid tests is constant, their sensitivity
strongly depends \replaced[id=K]{on the timing of the rapid test relative to the start of
infectiousness}{on whether the tested individual is already infectious and if so for how
long he has been infectious}. Before the onset of infectiousness the sensitivity is very
low (35\%). On the first day of infectiousness it is much higher (88\%) but still lower
than during the remaining infectious period (92\%). After infectiousness stops, the
sensitivity drops to 50 \%.

@@

We do not distinguish between self administered rapid tests and those that are
administered by medical personnel. While there were concerns that self administered
tests are less reliable, a recent study has found no basis for this
concern.\comment[id=J]{cite charite study on self administered tests}

While rapid tests do not directly enter official case numbers, 82\%
($\chi_{confirmation}$) of positively tested individuals seek a PCR test
\citep{Betsch2021}.\comment[id=J]{Need to link to data appendix once the number is there
and maybe mention the number}\comment[id=K]{Not mentioned in the data section.}
Importantly, those PCR tests are made in addition to the tests that would have been done
otherwise. Section~\ref{subsec:results_share_known_cases} discusses the effect of rapid
tests on the share of detected cases.

>>>>

Having a realistic model of PCR and rapid tests is crucial for two reasons: Firstly, only
via a testing model can the simulated infections from the model be made comparable to
official case numbers. Secondly, individuals with undetected or not yet detected
infections are an important driver of the pandemic.

@@

Therefore, we build a simpler model of PCR and rapid tests that can be calibrated with
available data on test demand and availability and -- nevertheless
-- can produce a share of undetected cases that varies over time and across age groups
and agrees with other estimates over the time periods where they are available.

@@

Sampling uniformly from the pool of symptomatic individuals ensures that age groups who
are more likely to develop symptoms are also more likely to receive tests. Thus, the
share of detected cases is much higher for the elderly than for children in time periods
where many tests are done because of symptoms.

@@

The second challenge is solved by mechanistic rapid test demand models for the
workplace, schools and by private individuals. The calibration of these models is
described in Section~\ref{subsec:rapid_test_demand}.
Figure~\ref{fig:antigen_tests_vaccinations} shows that the number of performed rapid
tests in the model fits the empirical data well (where empirical data is available).

In contrast to PCR tests, rapid tests are not perfect and can be falsely positive or
falsely negative. While the specificity of rapid tests is constant, their sensitivity
strongly depends on the timing of the rapid test relative to the start of infectiousness.
Before the onset of infectiousness the sensitivity is very low (35\%). On the first day
of infectiousness it is much higher (88\%) but still lower than during the remaining
infectious period (92\%). After infectiousness stops, the sensitivity drops to 50 \%.

@@

We do not distinguish between self administered rapid tests and those that are
administered by medical personnel. While there were concerns that self administered
tests are less reliable, a recent study has found no basis for this
concern \citep{Lindner2020}.

While rapid tests do not directly enter official case numbers, 82\%
($\chi_{confirmation}$) of positively tested individuals seek a PCR test
\citep{Betsch2021}. Importantly, those PCR tests are made in addition to the tests that
would have been done otherwise. Section~\ref{subsec:results_share_known_cases} discusses
the effect of rapid tests on the share of detected cases.
